Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-05-18 main.tex
Second draft completed

\begin{abstract}%% (Must be 250 Words)
% In this paper, we introduce a new method of clustering of high red-shift galaxies, based on their spectral energy distributions (SED)s. We use unsupervised self organizing map(SOM) to train an artificial neural network to categorize SEDs of galaxies. We utilize as spectral template as a training set, and trained networks to be able to clustered galaxies based on the template. We cluster a sample of 142 galaxies with 0.5< z <1 using the trained network. We train networks with various sizes and properties to investigate the nature of the 142 sample galaxies. For each network, we cluster the sample of 142 galaxies and visualise their properties. In order to test new classifications,we compare physical properties of the galaxies in each cluster. We compare our results with  clustering  results  from  other  artificial  neural  networks,  and  with  the  original template classification. We conclude that SOM is a very useful method to be used in classifying galaxies based on their SEDs. It can be used to find morphology of the high red-shift galaxies, and find a new class of SEDs.
In this paper, we introduce a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
Artificial neural networks provide us a reliable method to cluster SEDs of galaxies.
We use an unsupervised self organizing map(SOM) as a training method to train networks with a sample of galaxies with SEDs between FUV to NIR wavelengths, which their morphological types are known.
Since information that can be extracted from each network depends on the size and dimension of the trained networks, in this project we train networks with different grids in 1D or 2D.
We visualise each trained network using a new version of SOM plots.
To test trained networks, we cluster a sample of 142 galaxies with 0.5 < $z$ < 1 using each of the trained networks.
We plot average SED of SEDs of galaxies in each neurons in 1D networks, to investigate the nature galaxies in new clusters.
For each network, we visualise the properties of galaxies in each neurons. 
We compare mean physical properties of the galaxies such as age, specific star formation rate, stellar mass, and FUV extinction, with each other and found a tight correlations between them.
Comparing our results with clustering results from supervised artificial neural networks, show us using SOM we can classify galaxies in between types of original spectral types.
As a result we have a power tool to classify morphological type of galaxies based on their SEDs which also can  identify galaxies with a new shape of SEDs.

@@

>>>>

\begin{abstract}%% (Must be 250 Words)
% In this paper, we introduce a new method of clustering of high red-shift galaxies, based on their spectral energy distributions (SED)s. We use unsupervised self organizing map(SOM) to train an artificial neural network to categorize SEDs of galaxies. We utilize as spectral template as a training set, and trained networks to be able to clustered galaxies based on the template. We cluster a sample of 142 galaxies with 0.5< z <1 using the trained network. We train networks with various sizes and properties to investigate the nature of the 142 sample galaxies. For each network, we cluster the sample of 142 galaxies and visualise their properties. In order to test new classifications,we compare physical properties of the galaxies in each cluster. We compare our results with  clustering  results  from  other  artificial  neural  networks,  and  with  the  original template classification. We conclude that SOM is a very useful method to be used in classifying galaxies based on their SEDs. It can be used to find morphology of the high red-shift galaxies, and find a new class of SEDs.
In this paper, we introduce a new method of clustering high red-shift galaxies, based on their spectral energy distributions (SED)s.
%Artificial neural networks provide us a reliable method to cluster SEDs of galaxies.
We use an unsupervised self organizing map(SOM) as a training method to train networks with a sample of galaxies with SEDs between FUV to NIR wavelengths, which their morphological types are known.
Since information that can be extracted from each network depends on the size and dimension of the trained networks, in this project we train networks with different grids in 1D or 2D.%%???
We visualise each trained network using a new version of SOM plots.
To test trained networks, we cluster a sample of 142 galaxies with 0.5 < $z$ < 1 using each of the trained networks.
We plot average SED of SEDs of galaxies in each neurons in 1D networks, to investigate the nature galaxies in new clusters.
For each network, we visualise the properties of galaxies in each neurons. %%%% combine 94 and 93 
We compare mean physical properties of the galaxies in each neuron such as age, specific star formation rate, stellar mass, and FUV extinction, with each other and found a tight correlations between them. 
Comparing our results with clustering results from supervised artificial neural networks, show us using SOM we can classify galaxies in between types of original spectral types. %%rephrase
As a result we have a power tool to classify spectral glaxies based on their SEDs which also can  identify galaxies with a new shape of SEDs.

@@

%%% what is the problem we are trying to solve in general! why do we want o classify thing in general, and what is wrong in exciting classification scheam
